An Overview of Distributed Version Control Systems

### 2010-06-08 laarsample.tex
Corregidas algunas cosas de redacción

Git, in particular, is based on Linux and originally didn't work work out of the box in Windows, 
but with Cygwin. 
Now there is a fork of Git that ports it to windows, but the linux heritage is 
shown and the installation includes a Bash shell. 
Git also includes a portable GUI written in Tk, invoked with command ``git gui'' 
but while it is simple and easy to use, it is very incomplete (for example, 
it doesn't include the ``pull'' operation, among others).

There are many other third-party GUIs for Git, but none of them has all available operations nor are them equally mature, 
in those cases, the command line is the only way to do them. One of the most complete GUIs is SmartGit, but 
requires to purchase a (rather inexpensive) licence for commercial usage. An alternative for Windows only 
is Tortoise-Git, which is a fork of Tortoise-SVN that shares the same look-and-feel, while supporting most of the 
Git operations. There are others GUIs but they are either very uncomplete or aren't really mature and have 
some kind of bugs (like git-cola) \cite{interfaces}.

>>>>

Git, in particular, is based on Linux and originally didn't work work out of the box in Windows, 
only by using Cygwin. 
There is now a Git fork which ports it to windows. However it still carries a linux heritage which is shown when the installation includes a Bash shell.
Git also includes a portable GUI written in Tk, invoked with command ``git gui'' 
but while it is simple and easy to use, it is very incomplete (for example, 
it doesn't include the ``pull'' operation, among others).

There are many other third-party GUIs for Git, but none of them has all available operations nor are they equally mature. 
In those cases, going back to the command line is the only way to do them. One of the most complete GUIs is SmartGit, but 
it requires to purchase a (rather inexpensive) licence for commercial usage. An alternative for Windows only 
is Tortoise-Git, which is a fork of Tortoise-SVN that shares the same look-and-feel, while supporting most of the 
Git operations. There are others GUIs but they are either very uncomplete or aren't really mature and have 
some kind of bugs (like git-cola) \cite{interfaces}.
